Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-10 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Syntax of CTLK}
\begin{definition} [Syntax of CTLK]\label{Syntax of CTLK}~\\
$~~~~~~~~~~~~~ \varphi ::= p \mid \neg \varphi \mid \varphi \vee
\varphi \mid EX \varphi  \mid E ( \varphi U \varphi) \mid EG
\varphi \mid K_i \varphi$\\
Where:
\begin{itemize}
\item $ p \in \Phi_p$ is an atomic proposition; \item The boolean
connectives $\neg$, and $\vee$ are defined in the usual way; \item
$E$ is the existential quantifier on paths; \item $X$, $U$, and
$G$ are CTL path modal connectives standing for ``next", ``until",
and ``globally" respectively; and \item The modal connective $K_i$
stands for ``knowledge for agent $i$".
\end{itemize}
\label {dfn: Syntax of CTLK}
\end{definition}
In this logic, \textbf{$K_i \varphi$ is read as ``agent $i$ knows
$\varphi"$.}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
Given the model $ \mathcal M$, the satisfaction of a CTLK formula
$ \varphi$ in a global state $ s$, denoted by $ (\mathcal M, s )
\models \varphi$, is recursively defined as follows:

\begin{itemize}
\item $ (\mathcal{M}, s ) \models p$ iff $ p \in \mathcal{V}(s)$;
\item $ (\mathcal{M}, s ) \models \neg \varphi$ iff $ (\mathcal{M}, s ) \nvDash \varphi$;
\item $ (\mathcal{M}, s ) \models \varphi \vee \psi$ iff $(\mathcal{M}, s ) \models \varphi$ or $(\mathcal{M}, s ) \models \psi$;
\item $ (\mathcal{M}, s ) \models EX \varphi $ iff there exists a path $\pi$ starting at $s$ such that $ (\mathcal{M}, \pi(1) ) \models \varphi$;
\item $ (\mathcal{M}, s ) \models E ( \varphi U \psi)$ iff there exists a path $\pi$ starting at $s$ such that for some $ k \geq 0$,
$ (\mathcal{M}, \pi(k) ) \models \psi$ and $ (\mathcal{M}, \pi(j) ) \models \varphi$ for all $ 0 \leq j < k$;

\end{itemize}
\label {dfn: Satisfaction of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Satisfaction of CTLK}
\begin{definition} [Satisfaction of CTLK]~\\
\begin{itemize}
\item $ (\mathcal{M}, s ) \models EG \varphi$ iff there exists a path $\pi$  starting at $s$ such that $ (\mathcal{M}, \pi(k) ) \models \varphi$ for all $ k \geq 0$;
\item $ (\mathcal{M}, s ) \models K_i \varphi $ iff for all global states $s' \in S$ such that $s \approx_i s'$, we have $(\mathcal{M}, s' ) \models \varphi $.
\end{itemize}
\label {dfn: Satisfaction of CTLK}
\end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Computation Tree Logic of Commitment (CTLC)}
CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
\begin{definition} [Model of CTLC]\label{Model of CTLC}
A model $\mathcal{M_C}=(S,I,R_t, \{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK).
\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
     1) $ l_i(s) = l_i(s') $ and 2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$.

>>>>

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties of valuation functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{red} additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{red} super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{red} weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
        \item {\color{red} subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}

    $\forall C_1,C_2 \subseteq N$
    \begin{itemize}
        \item {\color{red} convex:} $v(C_1) + v(C_2) \leq v(C_1 \bigcup C_2) + v(C_1 \bigcap C_2)$ Convexity has important properties in cooperative game theory solution concepts.
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution properties}
    Let $x \in R^n$ be a solution of the TU game $(N,v)$
    \begin{itemize}
        \item {\color{red} Feasible solution:} $\sum_{i \in N} x(i) \leq v(N)$
        \item {\color{red} Efficiency:} $x(N) = v(N)$
        \begin{itemize}
            \item the payoff distribution is an allocation of the entire worth of the grand coalition to all agents
        \end{itemize}
        \item {\color{red} Individual rationality:} $\forall i \in N, x(i) \geq v(\{i\})$
        \begin{itemize}
            \item player obtains at least its self-value of payoff
        \end{itemize}
        \item {\color{red} Group rationality:} $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{itemize}

    \vspace{0.2cm}

    An {\color{red} imputation} is a payoff distribution $x$ that is efficient and individual rational.

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item 3 can say to 1 ``let's form $\{1,3\}$ and share (40,0,40)''
        \item 2 can say to 1 ``let's form $\{1,2\}$ and share (45,45,0)''
        \item 3 can say to 2 ``OK, let's form $\{2,3\}$ and share (0,46,24)''
        \item 1 can say to 2 and 3, ``fine! $\{1,2,3\}$ and (33,47,25)''
        \item ...what is a good solution?
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Computation Tree Logic of Commitment (CTLC)}
CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
\begin{definition} [Model of CTLC]\label{Model of CTLC}
A model $\mathcal{M_C}=(S,I,R_t, \{\sim _{i \rightarrow j}|{(i,j)\in \mathcal{A}^2}\},\mathcal{V})$ that belongs to the set of all models $\mathbb{M}$ is a tuple, where:
\begin {itemize}
\item $S, I, R_t$ and $\mathcal{V}$ are the same as in Definition (Model of CTLK).
\item For each pair $(i, j) \in \mathcal{A}^2 $, $\sim _{i \rightarrow j} \subseteq S \times S $ is the social accessibility relation defined by $ s \sim _{i \rightarrow j} s' $ iff
     1) $ l_i(s) = l_i(s') $ and 2) $ Var_i \cap Var_j \neq \emptyset $ such that  $ \forall x \in Var_i \cap Var_j $ we have $ l_i^x(s) = l_j^x(s') $ and $ \forall y \in Var_j - Var_i $ we have $ l_j^y(s) = l_j^y(s')$.
